Kaggle

### 2020-08-23 inst/analysis/analysis_stable.Rmd
Add makefile for the pipeline

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
        self_contained: no
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
    data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/summarized-packages.fst"
    #data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"
    # The trace data on all CRAN does not have all the columns of the smaller corpus. The analysis will fail for the big corpus.

@@

source("inc/latextags.R")
create_tags(path("/var/lib/R/project-evalR/revalstudy/inst/data", "analysisStable.tex"), prefix="", default=TRUE)
```

@@

The analysis is being performed on dataset read from file `r params$data_filepath`.

```{r file-info, echo=FALSE}
file_info(params$data_filepath)
```

```{r load-data, echo=FALSE}
eval_calls <-
    read_fst(params$data_filepath) %>%
    as_tibble() %>%
    mutate(eval_call_package = extract_package_name(eval_call_srcref, file))

>>>>

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
        self_contained: no
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR

@@

source("inc/paths.R")
source("inc/latextags.R")
create_tags(path(TAGS_DIR, "analysisStable.tex"), prefix="", default=TRUE)

data_filepath <- EVALS_SUM_PKGS_FILE
#data_filepath <- "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"
# The trace data on all CRAN does not have all the columns of the smaller corpus. The analysis will fail for the big corpus.
```

@@

The analysis is being performed on dataset read from file `r data_filepath`.

```{r file-info, echo=FALSE}
file_info(data_filepath)
```

```{r load-data, echo=FALSE}
eval_calls <-
    read_fst(data_filepath) %>%
    as_tibble() %>%
    mutate(eval_call_package = extract_package_name(eval_call_srcref, file))

### 2020-08-23 inst/analysis/corpus-analysis.Rmd
Add makefile for the pipeline

---
title: "Corpus Analysis"
output: 
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

>>>>

---
title: "Corpus Analysis"
output: html_document
params:
  base_dir: /var/lib/R/project-evalR
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
for (x in c(
  "dplyr", 
  "DT",
  "fs",
  "fst",
  "lubridate",
  "readr",
  "purrr",
  "stringr",
  "tidyr"
  )) {
  suppressPackageStartupMessages(library(x, character.only=TRUE))
}

knitr::opts_chunk$set(echo = TRUE)

# TODO: move into the package
source("inc/paths.R")
source("inc/setup.R")
source("inc/latextags.R")

create_tags(path(TAGS_DIR, "corpus.tex"), prefix="", default=TRUE)
```

## Load data

```{r}

```

## Corpus Overview

### Table

```{r summary}
overview_table(
  r("corpus", corpus),
  r("runnable code",        sum(corpus$runnable_code, na.rm=T)),
  r("examples code",        sum(corpus$runnable_code_examples, na.rm=T)),
  r("tests code",           sum(corpus$runnable_code_tests, na.rm=T)),
  r("vignettes code",       sum(corpus$runnable_code_vignettes , na.rm=T)),
  r("mean expr coverage",   percent(mean(corpus$coverage_expr))),
  r("median expr coverage", percent(median(corpus$coverage_expr))),
  r("with R code",          filter(corpus, package_r_code > 0)),
  r("R code",               sum(corpus$package_r_code, na.rm=T)),
  r("with native code",     filter(corpus, package_native_code > 0)),
  r("native code",          sum(corpus$package_native_code, na.rm=T)),
  r("functions",            sum(corpus$funs, na.rm=T)),
  r("public functions",     sum(corpus$funs_public, na.rm=T)),
  r("private functions",    sum(corpus$funs_private, na.rm=T)),
  r("revdes",               sum(corpus$revdeps)),
  r("mean revdes",          mean(corpus$revdeps)),
  r("median revdes",        median(corpus$revdeps)),
  r("runtime",              as.duration(sum(corpus$runnable_time))),
  r("mean runtime",         as.duration(mean(corpus$runnable_time))),
  r("median runtime",       as.duration(median(corpus$runnable_time)))
)
```

### Plots

```{r plot corpus}
coverage_mean <- mean(df$coverage_expr)
coverage_median <- median(df$coverage_expr)
revdeps_mean <- mean(df$revdeps)
revdeps_median <- median(df$revdeps)

df %>%
  mutate(
    outlier=package_code > PACKAGE_SIZE_OUTLIER,
    label=if_else(outlier, str_glue("{package}"), as.character(NA))
  ) %>%
  ggplot(
    aes(
      x=coverage_expr, 
      y=revdeps,
      label=label,
      size=package_code
    )
  ) +
  geom_point(alpha=.6) +
  geom_text(size=3, check_overlap = T, vjust=1.5, na.rm = TRUE) +

  geom_hline(aes(yintercept=revdeps_mean), linetype="dashed", color="red", size=0.2) +
  geom_vline(aes(xintercept=coverage_mean), linetype="dashed", color="red", size=0.2) +

  scale_x_continuous(limits = c(params$min_coverage, 1), labels = scales::percent) + 
  scale_y_log10(labels = scales::comma) +
  scale_size(range = c(.1, 3), labels = scales::comma) +
    theme(
    legend.position=c(0.2, 0.85),
    legend.box="horizontal",
    legend.box.background = element_rect(fill="white", size=0.1)
  ) +
  labs(
    x="Code coverage", 
    y="Number of reverse dependencies (log)", 
    size="Code size",
    linetype=""
  ) +
  guides(
    size=guide_legend(order=1),
    color=guide_legend(order=2),
    linetype=F
  )

ggsave(CORPUS_PLOT)
```

### List of corpus packages

```{r list of packages, eval=FALSE}
datatable(
  corpus, 
  filter="top", 
  options=list(
    pageLength=50,
    autoWidth=TRUE
  )
)
```

## Kaggle

```{r, eval=FALSE}
parallel_log <- 
  read_csv(PARALLEL_LOG_FILE)

parallel_log %>%
  mutate(
    output=show_url(path(V1, "run.R.out"))
  ) %>%
  my_datatable(escape=FALSE)
```

### 2020-08-23 inst/analysis/enrich_dataset.Rmd
Add makefile for the pipeline

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced/calls-final.fst"
  data_kagglepath: "/var/lib/R/project-evalR/kaggle-korpus/run/titanic/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

source("insights.R", local = knitr::knit_global())

source("preprocess.R", local = knitr::knit_global())
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

The analysis is being performed on a dataset read from file `r params$data_filepath`.

```{r file-info, echo=FALSE}
file_info(params$data_filepath)
```

```{r load-data, echo=FALSE}
eval_calls_raw <-
    read_fst(params$data_filepath) %>%
    as_tibble() %>%
    mutate(corpus = "cran")

eval_calls_kaggle_raw <- 
  read_fst(params$data_kagglepath) %>%
  as_tibble() %>% 
  mutate(corpus = "kaggle")

@@

```{r write_back}
write_fst(eval_calls, paste0(params$data_dirpath, "raws.fst"))

write_fst(eval_calls_core, paste0(params$data_dirpath, "summarized-core.fst"))

write_fst(eval_calls_packages, paste0(params$data_dirpath, "summarized-packages.fst"))

write_fst(eval_calls_kaggle, paste0(params$data_dirpath, "summarized-kaggle.fst"))
```

>>>>

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

source("inc/paths.R")
source("insights.R", local = knitr::knit_global())
source("preprocess.R", local = knitr::knit_global())
```

@@

The analysis is being performed on a dataset read from file `r CALLS_FINAL_FILE`.

```{r file-info, echo=FALSE}
file_info(CALLS_FINAL_FILE)
```

```{r load-data, echo=FALSE}
eval_calls_raw <-
    read_fst(CALLS_FINAL_FILE) %>%
    as_tibble() %>%
    mutate(corpus = "cran")

eval_calls_kaggle_raw <- 
  read_fst(KAGGLE_CALLS_FINAL_FILE) %>%
  as_tibble() %>% 
  mutate(corpus = "kaggle")

@@

```{r write_back}
write_fst(eval_calls, EVALS_RAW_FILE)

write_fst(eval_calls_core, EVALS_SUM_CORE_FILE)

write_fst(eval_calls_packages, EVALS_SUM_PKGS_FILE)

write_fst(eval_calls_kaggle, EVALS_SUM_KAGGLE_FILE)
```

### 2020-08-23 inst/analysis/kaggle.Rmd
Add makefile for the pipeline

---
title: "Kaggle"
output: html_document
params:
  base_dir: /home/rstudio/evalR
  hostname: prl2
  port: 8788
  competitions:
    - titanic
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
for (x in c(
  "dplyr", 
  "DT", 
  "fs",
  "fst",
  "purrr",
  "readr",
  "rjson",
  "runr",
  "stringr",
  "tibble"
  )) {
  suppressPackageStartupMessages(library(x, character.only=TRUE))
}

@@

# TODO: move into the package
source("inc/paths.R")
source("inc/setup.R")
source("inc/latextags.R")

create_tags(path(TAGS_DIR, "kaggle.tex"), prefix="Kaggle", default=TRUE)

KAGGLE_KERNELS_DIR  <- path(params$base_dir, "run", "kaggle-kernels", "notebooks", "r", "kernels")
KAGGLE_DATASETS_DIR <- path(params$base_dir, "run", "kaggle-datasets")
KAGGLE_RUN_DIR      <- path(params$base_dir, "run", "kaggle-run")

KERNELS_FILE      <- path(KAGGLE_RUN_DIR, "kernels.csv")
SCRIPTS_FILE      <- path(KAGGLE_RUN_DIR, "scripts.txt")
PARALLEL_LOG_FILE <- path(KAGGLE_RUN_DIR, "parallel.csv")
```

@@

process <- function(x) {
  run_path <- path(KAGGLE_RUN_DIR, x$competition, basename(x$path))
  code_file <- path(x$path, "script", x$code_file)
  run_code_file <- path(run_path, "run.R")

  dir_create(run_path)

@@

@@

```{r delete run dir}
if (dir_exists(KAGGLE_RUN_DIR)) dir_delete(KAGGLE_RUN_DIR)
```

```{r extract kernels}
extraction <- 
  known_competitions %>%
  rowwise() %>%
  do({
    tryCatch({
      tibble(id=.$id, run_file=process(.))
    }, error=function(e) {
      tibble(id=.$id, error=e$message)
    })
  })
```

@@

```{r compute sloc}
sloc <- map_dfr(path(KAGGLE_RUN_DIR, params$competitions), function(x) {
  out <- system2("cloc", c("--by-file-by-lang", "-q", "--csv", shQuote(x)), stdout = TRUE)  
  out <- out[2:(length(out)-4)]
  out[1] <- "language,filename,blank,comment,code"
  df <- read_csv(out)
}) %>%
  mutate(
    kernel=basename(dirname(filename))
  ) %>%
  select(kernel, code)

@@

```{r add sloc to the kernels_supported set}
kernels_supported <- left_join(kernels_supported, sloc, by=c("id"="kernel"))
```

```{r kernels with no R code or duplication}
kernels_duplicated <- filter(kernels_supported, is.na(code) | code == 0)
kernels_runnable <- filter(kernels_supported, code > 0)
```

```{r display duplicated or empty kernels}
kernels_duplicated %>% 
  mutate(
    code_file=show_url(file.path(KAGGLE_KERNELS_DIR, id, "script", code_file)),
    path=show_url(path),
    run_file=show_url(run_file)
  ) %>%
  select(id, competition, path, run_file, language, code_file) %>%
  my_datatable(escape=FALSE)
```

```{r}
write_csv(kernels_runnable, KERNELS_FILE)
write_lines(dirname(kernels_runnable$run_file), SCRIPTS_FILE)
```

@@

```{r run}
Sys.unsetenv("R_HOME")
run <- system2(
  "parallel",
  c(
    "-a", SCRIPTS_FILE,
    "--bar",
    "--jobs", parallel::detectCores(),
    "--results", PARALLEL_LOG_FILE,
    "--tagstring", "{/}",
    "--timeout", "1h",
    "--workdir", "{1}/",
    file.path(R_DIR, "bin", "R"), "CMD", "BATCH", "{1}/run.R", "{1}/run.R.out"
  )
)
```

```{r load results}
calls <- kernels_runnable %>%
  do({
    bd <- basename(.$run_file)
    tryCatch({
      df <- as_tibble(read_fst(path(bd, "calls.fst")))
      add_column(df, id=.$id, .before=1)
    }, error=function(e) {
      tibble(id=.$id, error=e$message)
    })
  })
```

```{r}
parallel_log <- 
  read_csv(PARALLEL_LOG_FILE)

parallel_log %>%
  mutate(
    output=show_url(path(V1, "run.R.out"))
  ) %>%
  my_datatable(escape=FALSE)
```

## Errors

>>>>

---
title: "Kaggle"
output: html_document
params:
  base_dir: /var/lib/R/project-evalR
  hostname: prl3
  port: 8788
  competitions:
    - titanic
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
for (x in c(
  "callr",
  "dplyr", 
  "DT", 
  "fs",
  "fst",
  "knitr",
  "purrr",
  "readr",
  "rjson",
  "rmarkdown",
  "runr",
  "stringr",
  "tibble"
  )) {
  suppressPackageStartupMessages(library(x, character.only=TRUE))
}

@@

# TODO: move into the package
source("inc/paths.R")
source("inc/setup.R")
source("inc/latextags.R")
```

```{r consts}
KAGGLE_KERNELS_DIR  <- path(RUN_DIR, "kaggle-kernels", "notebooks", "r", "kernels")
KAGGLE_DATASETS_DIR <- path(RUN_DIR, "kaggle-datasets")
KAGGLE_RUN_DIR      <- path(RUN_DIR, "kaggle-run")

KERNELS_FILE      <- path(KAGGLE_RUN_DIR, "kernels.csv")
SCRIPTS_FILE      <- path(KAGGLE_RUN_DIR, "scripts.txt")
PARALLEL_LOG_FILE <- path(KAGGLE_RUN_DIR, "parallel.log")
```

@@

extract_kernel_code <- function(path, code_file, competition) {
  run_path <- path(KAGGLE_RUN_DIR, competition, basename(path))
  code_file <- path(path, "script", code_file)
  run_code_file <- path(run_path, "run.R")

  if (!dir_exists(run_path)) dir_create(run_path)

@@

## Description

This notebook prepares the kaggle kernels to be run with the eval tracing framework.

### Input

- `r KAGGLE_DATASETS_DIR` - directory with kaggle datasets
- `r KAGGLE_KERNELS_DIR` - directory with kaggle kernels

### Output

- `r KAGGLE_RUN_DIR` - directory with prepared kernels to be run
- command to run the datasets

### Load kernels

@@

```{r delete run dir}
if (dir_exists(KAGGLE_RUN_DIR)) {
  warning("*** ", KAGGLE_RUN_DIR, " exists")
}
```

```{r extract kernels}
extraction_lst <- pbapply::pbapply(known_competitions, 1, cl=16, function(x) {
    tryCatch({
      tibble(id=x["id"], run_file=extract_kernel_code(x["path"], x["code_file"], x["competition"]))
    }, error=function(e) {
      tibble(id=x["id"], error=e$message)
    })
})
extraction <- bind_rows(extraction_lst)
```

@@

```{r compute sloc}
sloc <- map_dfr(path(KAGGLE_RUN_DIR, params$competitions), function(x) {
  out <- system2("cloc", c("--include-lang=R", "--by-file-by-lang", "-q", "--csv", shQuote(x)), stdout = TRUE)  
  out_r <- out[startsWith(out, "R,")]
  out_csv <- c("language,filename,blank,comment,code", out_r)
  df <- read_csv(out_csv)
}) %>%
  mutate(
    kernel=basename(dirname(filename))
  ) %>%
  select(kernel, code)

@@

```{r add sloc to the kernels_supported set}
kernels_supported <- 
  kernels_supported %>%
  left_join(sloc, by=c("id"="kernel")) %>%
  mutate(runnable=ifelse(is.na(code), FALSE, code > 0))
```

```{r display duplicated or empty kernels}
filter(kernels_supported, !runnable) %>% 
  mutate(
    code_file=show_url(file.path(KAGGLE_KERNELS_DIR, id, "script", code_file)),
    path=show_url(path),
    run_file=show_url(run_file)
  ) %>%
  select(id, competition, path, code, run_file, language, code_file) %>%
  my_datatable(escape=FALSE)
```

```{r}
kernels_runnable <- filter(kernels_supported, runnable)
write_csv(kernels_supported, KERNELS_FILE)
write_lines(dirname(kernels_runnable$run_file), SCRIPTS_FILE)
```

```{r}
count(kernels_supported, runnable)
```

@@

Run the following command from the `r params$base_dir` directory:

```{r}
cat("cd", shQuote(params$base_dir))

cat("parallel",
    "-a", shQuote(SCRIPTS_FILE),
    "--bar",
    "--jobs", parallel::detectCores(),
    "--results", shQuote(PARALLEL_LOG_FILE),
    "--tagstring", shQuote("{/}"),
    "--timeout", "1h",
    "--workdir", shQuote("{1}/"),
    path(R_DIR, "bin", "R"), "CMD", "BATCH", shQuote("{1}/run.R"), shQuote("{1}/run.R.out"), 
    "\n"
)

cat("runr/inst/merge-fst.R", "run/kaggle-run", "calls.fst", "ERROR.fst", "\n")
```
